\chapter{Design}

\section{Overall System Design}

\subsection{Short description of the main parts of the system}
\begin{itemize}
\item Home
This system will display the buttons required to  access the rest of the program and exit the program
\item Match
This system will display the details of a all the past matches that have been entered into the system. 
\item Player 
This system  will display all the details that have been entered by the user on an individual player.  
\item Team Sheet
This system will display the selected players in the selected formation, it will also have the substitutes listed to one side of the screen. The user will also be able to swap players in and out of the team sheet. Once the one user is happy with the team sheet they will be able to save it to the database for future reference. 
\item Goals
This system will display a list of goals from all past games that have been entered into the system, it will include bas details such as the scorer, the match it was scored in and the quantity.
\item Squad
This system will display a list of all the players in the squad.
\item Add Player
This system will ask for the user to input the basic details of a new player, such as name and position. These details will all be entered into text boxes.
\item Add Goals
This system will ask for the user to select the match and goal scorer from a drop down menu, The user will then have to enter the quantity scored by the selected player in the selected game. 
\item Add Match
This system will ask for the user to input the basic details of a recent match, such as the result and the opposition.

\end{itemize}
\section{User Interface Designs}

\section{Hardware Specification}
The system will need to run on a desktop computer, a laptop and on a tablet. It will need to run on the computers at 1360x768, in a 16:9 aspect ratio screen as well the IPad's 1024x768-pixel display, in a 4:3 aspect ratio. A keyboard will be needed for input as well as a pointer device to navigate around the system. A display will be used for the output of the program. The data for the program will be held on a hard drive.
\section{Program Structure}

\subsection{Top-down design structure charts}

\subsection{Algorithms in pseudo-code for each data transformation process}

\subsection{Object Diagrams}

\subsection{Class Definitions}

\section{Prototyping}

\section{Definition of Data Requirements}

\subsection{Identification of all data input items}
\begin{itemize}
\item Player first name
\item Player second name
\item Player rating
\item Player email
\item Player position
\item Player availability
\item Match Date
\item Match opposition
\item Match result
\item Goal Quantity 

\end{itemize}

\subsection{Identification of all data output items}
\begin{itemize}
\item team sheet
\item goal table
\item
\subsection{Explanation of how data output items are generated}
\begin{itemize}
\item The team sheet will be generated by the user selecting players from the player table. The player data will have been previously entered by the user. 
\end{itemize}
\subsection{Data Dictionary}
\begin{table}[H]
\centering
%\begin{tabular}{|p{2.5cm}|p{1cm}|p{1.5cm}|p{2.5cm}|p{2.5cm}|p{2.5cm}|} 
\begin{tabular}{|l|l|l|l|l|l|} 
\hline
Name            & Data Type & Length   & Validation                    & Example Data    & Comment                        \\ \hline
PlayerID        & Integer   & 3 Digits & 3 Digits, Must exist          & 123             & Unique to each player          \\ \hline
PlayerForename  & String    & 15 Chars & Minimum of 3 digits           & Harry           & First name, capital first char \\ \hline
PlayerSurname   & String    & 20 Chars & Minimum of 3 digits           & West            & Surname, capital first char    \\ \hline
PlayerPosition  & String    & 2 Chars  & Must be 2 chars               & GK              & In caps                        \\ \hline
PlayerRating    & Integer   & 2 Digits & Maximum of 2 digits           & 8               & Most likely to only be 1 digit \\ \hline
PlayerEmail     & String    & 50 Chars & Must have an @                & Hwest@gmail.com & Contact for the player         \\ \hline
MatchID         & Integer   & 3 Digits & 3 digits, must exist          & 869             & Unique to match                \\ \hline
MatchDate       & String    & 8 Chars  & Must exist                    & 23/09/14        & Date of the match              \\ \hline
MatchResult     & String    & 1 Chars  & Must exist                    & W               & W=Win, L=lose, D=Draw          \\ \hline
MatchOpposition & String    & 20 Chars & Minimum of 3 digits           & Milton          & Opposition name                \\ \hline
GoalQuantity    & Integer   & 2 Digits & At least one digit must exist & 2               & 99\% will only be one digit    \\ \hline
\end{tabular}
\end{table}
\subsection{Identification of appropriate storage media}

\section{Database Design}

\subsection{Normalisation}

\subsubsection{ER Diagrams}

\subsubsection{Entity Descriptions}

\subsubsection{1NF to 3NF}

\subsection{SQL Queries}

\section{Security and Integrity of the System and Data}

\subsection{Security and Integrity of Data}

\subsection{System Security}

\section{Validation}

\section{Testing}

