\chapter{Analysis}

\section{Introduction}

\subsection{Client Identification}
My client is John West, He is the manager of Waterbeach colts Football Clubs U16 team.  He has a high level of knowledge on computers, as he uses them on a daily basis within his job. He uses computers for a variety of tasks, ranging from basic to advanced. He mainly uses Windows systems however he has used a Mac in the past. John requires a team management program so that he can easily manage his team.
\subsection{Define the current system}
The current system is done with pen and paper. A computer is used for contacting the players. The client has to manually collect all the computer data and copy it down to paper. The rest of the data that is required is all from memory. Currently the client makes note of who is/isn't available on paper. He collects this data from email replies.  He then works out where players can play and sorts out a team sheet for the upcoming game.
\subsection{Describe the problems}
There is no tracking for who has replied to the emails and who hasn't, this is one problem.  Another is that most the data comes from the clients memory; this can be slow as it's easy to forget a certain item/criteria momentarily. Due to using pen and paper, the current system gets rather messy after a few team sheets are created. It is also prone to go missing. Paper waste is also high making it environmentally unfriendly.

\subsection{Section appendix}
What data or information is recorded in the current system?
-Nothing is physically recorded. I recall it all from memory.
What data or information is to be recorded in the proposed system? How much data will the proposed system record?
-The proposed system is going to hold Player and Match data. The Player data will include contact information as well as positions and match stats. The Match data will include results,fixtures,goals for/against etc.
How frequently will the data need to be updated?
-The data will need to be updated on a weekly basis(after a match is played) unless there is a change in player contact information then it will need to be updated more frequently. 
Will new records need to be added or old ones deleted? How often?
-New records will need to be added when a player joins the club, and records will need to be deleted when players leave. This shouldn't be very often.
Will the changes come in batches or in ones and twos?
-The changes should come in small batches as players can only join/leave in a certain period.
How important is the data or information that is recorded?
- The data is very important because without it the system wouldn't be helpful. 
What inputs are required for the proposed system?
-Initially all the data will be required. On a weekly basis only 'Who's available' will be required.
What are the outputs from the current system?
-A rough paper copy of the team sheet. 
What outputs will be required from the proposed system?
-A more detailed team sheet. That can be clearly read and understood.
Are hard copies required?
-Yes as I cant take my computer to games. 
How often will outputs be required?
-Outputs will be required on a weekly basis.
Is security an issues?
-The system will store personal data (contact information)
Should there be restricted access to particular areas?
-No
How are exceptions and errors handled in the current system?
-If an error occurs then i have to restart. 
Does the user have a particular solution in mind?
-I have an idea of what i want it to look like. 
\section{Investigation}

\subsection{The current system}

\subsubsection{Data sources and destinations}

\subsubsection{Algorithms}

\subsubsection{Data flow diagram}

\subsubsection{Input Forms, Output Forms, Report Formats}

\subsection{The proposed system}
Proposed system is going to set out the team sheet, show injuries and possible replacements. It will also store all the information of players with attributes and contact information. It should also include an email reply system to show who's replied and available for upcoming events.  New records will need to be added every time a new player joins and a record will need to be deleted every time a player leaves.

\subsubsection{Data sources and destinations}

\subsubsection{Data flow diagram}

\subsubsection{Data dictionary}

\subsubsection{Volumetrics}

\section{Objectives}

\subsection{General Objectives}

\subsection{Specific Objectives}

\subsection{Core Objectives}

\subsection{Other Objectives}

\section{ER Diagrams and Descriptions}

\subsection{ER Diagram}

\subsection{Entity Descriptions}

\section{Object Analysis}

\subsection{Object Listing}

\subsection{Relationship diagrams}

\subsection{Class definitions}

\section{Other Abstractions and Graphs}

\section{Constraints}

\subsection{Hardware}
The client has a windows desktop PC and laptop along with an Ipad.
\subsection{Software}
The client has left it to me to choose the software. 
\subsection{Time}
There is a project deadline set by the teacher. 
\subsection{User Knowledge}
The user has a very large amount of knowledge as he uses computers on a daily basis. This includes basic and complex tasks. 

\subsection{Access restrictions}
Only he will be allowed access to the system as it contains personal information. 

\section{Limitations}

\subsection{Areas which will not be included in computerisation}

\subsection{Areas considered for future computerisation}

\section{Solutions}

\subsection{Alternative solutions}

\subsection{Justification of chosen solution}